si: code and prose exploring Spatial Interaction models

### 2022-04-15 README.qmd
updates readme

---
# format: html
format: gfm
number-sections: true
title: "si: code and prose exploring Spatial Interaction models"
bibliography: references.bib
execute:
  cache: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(cache = TRUE)
```

>>>>

---
# format: html
format: gfm
number-sections: true
title: "si: code and prose exploring Spatial Interaction models"
bibliography: data-raw/references.bib
execute:
  cache: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(cache = TRUE,
  fig.path = "man/figures/README-")
```
